Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-07-08 doc/main_jfm.tex
updates
working on BIE sections

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}

@@

@@

\begin{equation}
\label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma (\tfrac{1}{2}|\nabla u|^2 \mathbf{I} - \nabla u\otimes \nabla u).
\end{equation}
%
The integration over boundaries gives force and torque due to the hydrophobic attraction and they are given by

\begin{equation}
\int_{\Gamma_i} {\bf T}\cdot \nu_i dS ,\quad \int_{\Gamma_i} ({\bf x}-{\bf a}_i)\times ({\bf T}\cdot \nu_i) dS,
\end{equation}
%
where ${\bf x}$ are points on the boundary $\Gamma_i$, ${\bf a}_i$ is the $i^{th}$ particle center, and $\nu_i$ is the outward normal to the $i^{th}$ particle.

@@

The governing equation of $N_b$-body bodies suspended in the domain $\Sigma$ is

\begin{gather}
	-\Delta {\bf u} + \mu\nabla p = 0 \qquad \text{in }\Sigma\\
	\nabla\cdot {\bf u}=0 \qquad \text{in }\Sigma\\
	{\bf u}({\bf x}) \to {\bf u}_\infty \quad \text{as}\quad |{\bf x}|\to \infty
\end{gather}
%
where ${\bf u}$ is the velocity, $p$ is the pressure, and ${\bf u}_\infty$ is the background flow. 
%
%\begin{gather}
%\int_{\Gamma_i}(\sigma_{hyd}+\sigma_\infty)\cdot {\bf n} ds = -{\bf F}_i \\
%	\int_{\Gamma_i}(\sigma_{hyd}+\sigma_\infty)\times({\bf x}-{\bf a}_i)\cdot {\bf n} ds =-\tau_i\\
%\end{gather}
%
The mobility problem for $N_b$-body system in a Stokes flow leads to a second-kind boundary integral equations (BIE) with a density function $\eta({\bf x}$ that is given by \cite{Lukas19}
\begin{equation}
\label{mobility}
\begin{aligned}
{\bf v}_i + &\omega_i\times({\bf x}-{\bf a}_i)\\
 =& -\frac12\eta({\bf x}) + D[\eta]({\bf x}) \\
&+ \sum_{i=1}^N\big({\bf S}({\bf x}, {\bf a}_i){\bf F}_i+ {\bf R}({\bf x}, {\bf a}_i)t_i\big)+{\bf u}_\infty, \quad {\bf x}\in\Gamma \\
\end{aligned}
\end{equation}
%
with two constraints 
%
\begin{center}
\begin{equation}
\label{mobility2}
\int_{\partial \Gamma_i}\eta\cdot \nu ds = {\bf 0},
\end{equation}
\end{center}
%
\begin{center}
\begin{equation}
\label{mobility3}
\int_{\partial \Gamma_i}\eta\times({\bf x}-{\bf a}_i)\cdot \nu ds ={\bf 0},
\end{equation}
\end{center}
%
where the two-dimensional Stokeslet and the Rotlet are
%
\begin{gather}
{\bf S}({\bf x}, {\bf a}) = \frac{1}{4\pi}\left(-\log(|({\bf x}-{\bf a})|){\bf I}+\frac{({\bf x}-{\bf a})\otimes({\bf x}-{\bf a})}{|({\bf x}-{\bf a})|^2}\right) \\ 
{\bf R}({\bf x},{\bf a})=\frac{({\bf x}-{\bf a})^\perp}{4\pi|({\bf x}-{\bf a})|^2}.
\end{gather}
%
%Here ${\bf r}={\bf x}-{\bf a}$ and $\rho=|{\bf r}|$.
${\bf F}_i$ and $t_i$ are particle force and torque calculated from action of hydrophobic attractions. From equations~\eqref{mobility}--\eqref{mobility3}, we have translational velocity ${\bf v}_i$, angular velocity $\omega_i$, and density function $\eta$ as unknowns.
This system of equations is then solvable with the use of an iterative method such as GMRES or conjugate gradient iterations.

@@

\section{\label{IEM}Integral Equation Method}

\subsection{Single Particle Validations}

@@

\subsubsection{Relaxtion}

@@

@@

\begin{figure}
\begin{center}
\includegraphics[height=2in]{ReducedArea.pdf}
\hspace{-0.5cm}
\includegraphics[height=2in]{ArcLength.pdf}
\end{center} 
  \caption{(a) Total arc lengths of the midplanes over time in different shear rates; (b) Reduced area transitions over time. 
A set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
A slower shear rate generates a faster convergence in the reduced area. 
  }
    \label{figure4}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=1.2in]{N116_ext_0.pdf}
\includegraphics[height=1.2in]{N116_ext_2500.pdf}
\includegraphics[height=1.2in]{N116_ext_5000.pdf}
\includegraphics[height=1.2in]{N116_ext_7500.pdf}
%\includegraphics[width=0.24\textwidth]{step0Pres.eps}
%\includegraphics[width=0.24\textwidth]{step2500Pres.eps}
%\includegraphics[width=0.24\textwidth]{step5000Pres.eps}
%\includegraphics[width=0.24\textwidth]{step7500Pres.eps}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple.
  }
    \label{figure8}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=1.2in]{N116_cont_a.pdf}
\includegraphics[height=1.2in]{N116_cont_b.pdf}
\includegraphics[height=1.2in]{N116_cont_c.pdf}
\includegraphics[height=1.2in]{N116_cont_d.pdf}
%\includegraphics[width=0.24\textwidth]{step0Pres.eps}
%\includegraphics[width=0.24\textwidth]{step2500Pres.eps}
%\includegraphics[width=0.24\textwidth]{step5000Pres.eps}
%\includegraphics[width=0.24\textwidth]{step7500Pres.eps}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; Continuum modeling.....
  }
    \label{figure8}
\end{figure}

@@

\section{Appendices}
The stress ${\bf T}$ contains the gradient of the double layer potential. This 
introduces an inherent difficulty in evaluating stress on the boundary.
To overcome the difficulty of evaluation on $\Sigma_p$, for instance, we decompose $u$ into singular and nonsingular parts:
\begin{equation}
u = u_p + v_p
\end{equation}
where  
\begin{equation}
u_p(x) = \int_{\Sigma_p} \frac{\partial G(x,y)}{\partial \nu} \eta(y) \,\dif S(y).
\end{equation}
It turns out that the contribution to the force and torque coming from the singular
part vanishes. In particular, we will prove the identity
\begin{equation}
\label{eq:recipforcetorque}
F_p + iG_p= \int_{\Sigma_p} \gamma ({\bf I}+i{\bf X})J_{p} \,\dif S
\end{equation}
where
 \begin{equation}
\label{eq:jumpstress1}
J_{p} = 2\rho^{-1} \eta  v_p \nu 
+ 2\rho \nabla \eta \cdot \tau_i(\nabla v_p \cdot \tau_i \nu -  \nabla v_p \cdot \nu \tau_i).
\end{equation}
Here $\nu$ is the unit normal, $\{\tau_i\}_{i=1}^2$ are orthonormal tangent vectors,
and ${\bf X}$ is the skew symmetric matrix with axial vector $x$, i.e.
\[X_{ij} = \varepsilon_{ikj}x_k,\quad {\bf X}v = x\times v\]
where $\boldsymbol{\varepsilon}$ is the third-order alternating tensor.
We employ the Einstein summation convention and use complex vectors to streamline the presentation, $i^2 = -1$.

@@

Using Lemma \ref{eq:stress_div_lemma}, we will establish that
\begin{equation}
  \label{eq:prejump}
  F_p + i G_p = \gamma \int_{\Sigma_p}  ({\bf U}_2\nu)^+ - ({\bf U}_2\nu)^-\,\dif S
\end{equation}
where ${\bf U}_j = ({\bf I} + i {\bf X}){\bf T}_j$ for $j = 1, 2, 3.$
The stress ${\bf U}_2$ has a jump discontinuity at $\Sigma_p.$
The plus and minus superscripts denote
the limit taken along points in $U_p^c$ and along points in $U_p$
respectively.
${\bf U}_1$ and ${\bf U}_3$ are real-analytic in a neighborhood of $\overline{U_p}$
and have no jump-discontinuity at $\Sigma_p$.
To derive \eqref{eq:prejump}, we expand
\begin{align*}
  F_p + i G_p
  &= \gamma \int_{\Sigma_p} {\bf T} \nu + ix \times {\bf T} \nu \,\dif S \\
  &= \gamma \int_{\Sigma_p}  {\bf U}_1\nu  + ({\bf U}_2\nu)^+ + {\bf U}_3\nu\,\dif S
\end{align*}
The function $u_p$ is real-analytic and
$\nabla \cdot {\bf U}_1 = 0$ throughout $\mathbb{R}^n \setminus U_p$.
By the divergence theorem, we get
\begin{equation*}
  \int_{\Sigma_p}  {\bf U}_1 \nu\,\dif S
  = \int_{\mathbb{R}^n \setminus U_p} \nabla \cdot {\bf U}_1 \,dx = 0.
\end{equation*}
Next, $v_p$ is real-analytic and
$\nabla \cdot {\bf U}_3 = 0$ in $U_p$. Therefore
\begin{equation*}
  \int_{\Sigma_p}  {\bf U}_3 \nu\,\dif S
  = -\int_{U_p} \nabla \cdot {\bf U}_3 \,dx = 0.
\end{equation*}
Finally, $\nabla \cdot {\bf U}_2= 0$ in $U_p$. This gives
\[
0 = -\int_{U_p} \nabla \cdot {\bf U}_2 \,dx = \int_{\Sigma_p}  ({\bf U}_2 \nu)^-\,\dif S.
\]
Combining the last four equations give \eqref{eq:prejump}.

\begin{proof}[Proof of \eqref{eq:recipforcetorque}]
  The main ingredients of the proof are the jump relations
  for $u_p$. For $x_0 \in \Sigma_p$,
  \begin{enumerate}
  \item $ \lim_{x \to x_0^\pm } u_p(x) = \pm\frac{1}{2}\eta(x_0) + (D\eta)(x_0)$
  \item $ \lim_{x \to x_0^+ } (\nabla u_p \cdot \nu) (x) = \lim_{x \to x_0^-} (\nabla u \cdot \nu)(x)$
  \end{enumerate}
  Furthermore,
  combining (i) and (ii) gives
  \begin{align*}
    \nabla u_p^+ - \nabla u_p^-
    &= \nabla (u_p^+ - u_p^-) \cdot t_i t_i +  (\nabla  u_p^+\cdot \nu  - \nabla u_p^- \cdot \nu) \nu\\
    &= \nabla \eta \cdot \tau_i \tau_i
  \end{align*}
  where $\{\tau_i\}_{i=1}^n$ are an orthonormal tangent vectors.
  We can use these relationships to derive an expression for the jump in
  normal stress.
  \begin{align*}
    &({\bf T}_2\nu)^+ - ({\bf T}_2\nu)^-
    \\
    &= 2\rho^{-1} u_p^+v_p \nu + 2\rho \nabla u_p^+ \cdot \nabla v_p \nu
    - 2 \rho \nabla u_p^+  \nabla v_p \cdot \nu
    - 2 \rho \nabla v_p  \nabla u_p^+ \cdot \nu\\
    &-2\rho^{-1} u_p^-v_p \nu - 2\rho \nabla u_p^- \cdot \nabla v_p \nu
    + 2 \rho \nabla u_p^-  \nabla v_p \cdot \nu
    + 2 \rho \nabla v_p  \nabla u_p^- \cdot \nu\\
    &= 2\rho^{-1} \eta v_p \nu + 2\rho \nabla \eta \cdot \tau_i \tau_i \cdot \nabla v_p \nu
    - 2\rho \nabla \eta \cdot \tau_i \tau_i \nabla v_p \cdot \nu + 0\\
    &= J_p.
  \end{align*}

  Applying the above relations to the integrand of \eqref{eq:prejump} yields
  \[
  ({\bf U}_2\nu)^+ - ({\bf U}_2\nu)^-
  =
  ({\bf I} + i {\bf X})(({\bf T}_2\nu)^+ - ({\bf T}_2\nu)^-)
  = ({\bf I} + i {\bf X})J_p
  \]
  This completes the proof of \eqref{eq:recipforcetorque}.
\end{proof}

%\bibliographystyle{jfm}
\bibliography{reference}% Produces the bibliography via BibTeX.

>>>>

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{todonotes}

@@

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}

@@

\begin{equation}
\label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  u|^2 \mathbf{I} - \nabla u\otimes \nabla u\right).
\end{equation}
%
The integration over boundaries gives force and torque due to the
hydrophobic attraction 
\begin{align}
  \label{eqn:hydrophobicAttraction}
  \FF_i = \int_{\bd \Gamma_i} {\bf T}\cdot \nnu_i \, dS, 
    \quad  \text{ and } \quad
  T_i = \int_{\Gamma_i} (\xx - \aa_i) \times ({\bf T} \cdot \nnu_i) dS,
\end{align}
%
where $\xx \in \Gamma_i$, $\aa_i$ is the $i^{th}$ particle center, and
$\nnu_i$ is the outward normal of the $i^{th}$ particle.

@@

The governing equations of $N_b$-body bodies suspended in the unbounded
domain $\Omega$ are
\begin{alignat}{3}
  -\Delta \uu + \mu\nabla p, &= 0 \qquad \qquad && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu &\to \uu_\infty, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $p$ is the pressure, and $\uu_\infty$ is
the background flow. Each particle $\Gamma_i$ with center $\aa_i$ is
assumed to be a rigid body, so its two-dimensional velocity can be
written as
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Therefore, the no-slip boundary condition of
the velocity field is 
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \bd\Gamma_i.
\end{align}
To determine the translational and angular velocities of each rigid
body, we impose a force balance and torque balance. Matching the total
force and torque in~\eqref{eqn:hydrophobicAttraction} with the
hydrodynamic force, we require
\begin{align}
  \label{eqn:force}
  \FF_i &= \int_{\bd\Gamma_i} \ssigma \cdot \nnu_i \, ds, \\
  \label{eqn:torque}
  T_i &= \int_{\bd\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, ds,
\end{align}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor.

@@

%%%
\section{\label{IEM}Integral Equation Method}
Since the fluid velocity is assumed to be Stokesian, it can be written
in terms of layer potentials. Following previous work of~\cite{Lukas19},
we represent the velocity as the sum of a double-layer potential and the
$N_b$ Stokeslets and Rotlets
\begin{align}
  \label{eqn:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy,
\end{align}
where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and Rotlet
centered at $\aa_i$ are
\begin{align}
  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log(\rho) + 
    \frac{\rr \otimes \rr}{\rho^2} \FF_i \right), \\
  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{\rho^2} T_i,
\end{align}
where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The Stokeslet is
torque-free and has force $\FF$, and the Rotlet force-free and has
torque $T$. Therefore, the velocity~\eqref{eqn:velocity} satisfies the
total force~\eqref{eqn:force} and torque~\eqref{eqn:torque} conditions
if the double-layer potential $\DD[\eeta]$ is force- and torque-free.
Matching the limit of~\eqref{eqn:velocity} with the rigid body motion,
and imposing that $\DD[\eeta]$ is force- and torque-free, the density
function $\eeta$, Stokeslet strength, $\FF_i$, and Rotlet strength $T_i$
satisfy
\begin{alignat}{3}
  \nonumber
  \vv_j + \omega_j (\xx - \aa_j)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eqn:SKIE}
    &+ \sum_{i=1}^{N_b} 
    \left(\SS(\xx,\aa_i) \FF_i + \RR(\xx,\aa_i) T_i\right),
    \quad &&\xx \in \bd \Gamma_j, \\
  \label{eqn:mobility1}
  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, ds &= {\bf 0}, 
  &&i = 1,\ldots,N_b, \\
  \label{eqn:mobility2}
  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu ds &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}
%
%The mobility problem for $N_b$-body system in a Stokes flow leads to a second-kind boundary integral equations (BIE) with a density function $\eta({\bf x}$ that is given by \cite{Lukas19}
%\begin{equation}
%\label{mobility}
%\begin{aligned}
%{\bf v}_i + &\omega_i\times({\bf x}-{\bf a}_i)\\
% =& -\frac12\eta({\bf x}) + D[\eta]({\bf x}) \\
%&+ \sum_{i=1}^N\big({\bf S}({\bf x}, {\bf a}_i){\bf F}_i+ {\bf R}({\bf x}, {\bf a}_i)t_i\big)+{\bf u}_\infty, \quad {\bf x}\in\Gamma \\
%\end{aligned}
%\end{equation}
%%
%with two constraints 
%%
%\begin{center}
%\begin{equation}
%\label{mobility2}
%\int_{\partial \Gamma_i}\eta\cdot \nnu ds = {\bf 0},
%\end{equation}
%\end{center}
%%
%\begin{center}
%\begin{equation}
%\label{mobility3}
%\int_{\partial \Gamma_i}\eta\times({\bf x}-{\bf a}_i)\cdot \nnu ds ={\bf 0},
%\end{equation}
%\end{center}
%%
%where the two-dimensional Stokeslet and the Rotlet are
%%
%\begin{gather}
%{\bf S}({\bf x}, {\bf a}) = \frac{1}{4\pi}\left(-\log(|({\bf x}-{\bf a})|){\bf I}+\frac{({\bf x}-{\bf a})\otimes({\bf x}-{\bf a})}{|({\bf x}-{\bf a})|^2}\right) \\ 
%{\bf R}({\bf x},{\bf a})=\frac{({\bf x}-{\bf a})^\perp}{4\pi|({\bf x}-{\bf a})|^2}.
%\end{gather}
%
%Here ${\bf r}={\bf x}-{\bf a}$ and $\rho=|{\bf r}|$.
Given a collection of particles with forces and torques calculated from
the hydrophobic interactions and the short range repulsion,
equations~\eqref{eqn:SKIE}--\eqref{eqn:mobility2} form a solvable set of
integral equations for the translational velocities $\vv_i$, the angular
velocities $\omega_i$, and the density function $\eeta$.

\todo[inline]{Talk about how to solve numerically. Quadrature, time
stepping, collocation, etc.}
This system of equations is then solved iteratively with block-diagonal
preconditioned GMRES.

%%%

\section{\label{validation}Model Validation}

\subsection{Jeffery Orbit}

@@

\subsection{Self-Assembly and Relaxtion}

@@

%%%

@@

\begin{figure}
\begin{center}
\hspace{-1cm}
\includegraphics[height=2in]{ReducedArea.pdf}
\hspace{-1cm}
\includegraphics[height=2in]{ArcLength.pdf}
\hspace{-1cm}
\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{(a) Total arc lengths of the midplanes over time in different shear rates; (b) Reduced area transitions over time. 
A set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
A slower shear rate generates a faster convergence in the reduced area. 
  }
    \label{figure4}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2.in]{N116_ext_0.pdf}
\includegraphics[height=2.in]{N116_ext_2500.pdf}\\
\includegraphics[height=2.in]{N116_ext_5000.pdf}
\includegraphics[height=2.in]{N116_ext_7500.pdf}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple.
  }
    \label{figure8}
\end{figure}

%\begin{figure}
%\centering
%\includegraphics[height=1.2in]{N116_cont_a.pdf}
%\includegraphics[height=1.2in]{N116_cont_b.pdf}
%\includegraphics[height=1.2in]{N116_cont_c.pdf}
%\includegraphics[height=1.2in]{N116_cont_d.pdf}
%  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; Continuum modeling.....
%  }
%    \label{figure8}
%\end{figure}

@@

\section{Appendices}
The stress ${\bf T}$ contains the gradient of the double layer potential. This 
introduces an inherent difficulty in evaluating stress on the boundary.
To overcome the difficulty of evaluation on $\Sigma_p$, for instance, we decompose $u$ into singular and nonsingular parts:
\begin{equation}
u = u_p + v_p
\end{equation}
where  
\begin{equation}
u_p(x) = \int_{\Sigma_p} \frac{\partial G(x,y)}{\partial \nnu} \eta(y) \,\dif S(y).
\end{equation}
It turns out that the contribution to the force and torque coming from the singular
part vanishes. In particular, we will prove the identity
\begin{equation}
\label{eq:recipforcetorque}
F_p + iG_p= \int_{\Sigma_p} \gamma ({\bf I}+i{\bf X})J_{p} \,\dif S
\end{equation}
where
 \begin{equation}
\label{eq:jumpstress1}
J_{p} = 2\rho^{-1} \eta  v_p \nnu 
+ 2\rho \nabla \eta \cdot \tau_i(\nabla v_p \cdot \tau_i \nnu -  \nabla
   v_p \cdot \nnu \tau_i).
\end{equation}
Here $\nnu$ is the unit normal, $\{\tau_i\}_{i=1}^2$ are orthonormal tangent vectors,
and ${\bf X}$ is the skew symmetric matrix with axial vector $x$, i.e.
\[X_{ij} = \varepsilon_{ikj}x_k,\quad {\bf X}v = x\times v\]
where $\boldsymbol{\varepsilon}$ is the third-order alternating tensor.
We employ the Einstein summation convention and use complex vectors to streamline the presentation, $i^2 = -1$.

@@

Using Lemma \ref{eq:stress_div_lemma}, we will establish that
\begin{equation}
  \label{eq:prejump}
  F_p + i G_p = \gamma \int_{\Sigma_p}  ({\bf U}_2\nnu)^+ - ({\bf
  U}_2\nnu)^-\,\dif S
\end{equation}
where ${\bf U}_j = ({\bf I} + i {\bf X}){\bf T}_j$ for $j = 1, 2, 3.$
The stress ${\bf U}_2$ has a jump discontinuity at $\Sigma_p.$
The plus and minus superscripts denote
the limit taken along points in $U_p^c$ and along points in $U_p$
respectively.
${\bf U}_1$ and ${\bf U}_3$ are real-analytic in a neighborhood of $\overline{U_p}$
and have no jump-discontinuity at $\Sigma_p$.
To derive \eqref{eq:prejump}, we expand
\begin{align*}
  F_p + i G_p
  &= \gamma \int_{\Sigma_p} {\bf T} \nnu + ix \times {\bf T} \nnu \,\dif S \\
  &= \gamma \int_{\Sigma_p}  {\bf U}_1\nnu  + ({\bf U}_2\nnu)^+ + {\bf
  U}_3\nnu\,\dif S
\end{align*}
The function $u_p$ is real-analytic and
$\nabla \cdot {\bf U}_1 = 0$ throughout $\mathbb{R}^n \setminus U_p$.
By the divergence theorem, we get
\begin{equation*}
  \int_{\Sigma_p}  {\bf U}_1 \nnu\,\dif S
  = \int_{\mathbb{R}^n \setminus U_p} \nabla \cdot {\bf U}_1 \,dx = 0.
\end{equation*}
Next, $v_p$ is real-analytic and
$\nabla \cdot {\bf U}_3 = 0$ in $U_p$. Therefore
\begin{equation*}
  \int_{\Sigma_p}  {\bf U}_3 \nnu\,\dif S
  = -\int_{U_p} \nabla \cdot {\bf U}_3 \,dx = 0.
\end{equation*}
Finally, $\nabla \cdot {\bf U}_2= 0$ in $U_p$. This gives
\[
0 = -\int_{U_p} \nabla \cdot {\bf U}_2 \,dx = \int_{\Sigma_p}  ({\bf
U}_2 \nnu)^-\,\dif S.
\]
Combining the last four equations give \eqref{eq:prejump}.

\begin{proof}[Proof of \eqref{eq:recipforcetorque}]
  The main ingredients of the proof are the jump relations
  for $u_p$. For $x_0 \in \Sigma_p$,
  \begin{enumerate}
  \item $ \lim_{x \to x_0^\pm } u_p(x) = \pm\frac{1}{2}\eta(x_0) + (D\eta)(x_0)$
  \item $ \lim_{x \to x_0^+ } (\nabla u_p \cdot \nnu) (x) = \lim_{x \to
    x_0^-} (\nabla u \cdot \nnu)(x)$
  \end{enumerate}
  Furthermore,
  combining (i) and (ii) gives
  \begin{align*}
    \nabla u_p^+ - \nabla u_p^-
    &= \nabla (u_p^+ - u_p^-) \cdot t_i t_i +  (\nabla  u_p^+\cdot
    \nnu  - \nabla u_p^- \cdot \nnu) \nnu\\
    &= \nabla \eta \cdot \tau_i \tau_i
  \end{align*}
  where $\{\tau_i\}_{i=1}^n$ are an orthonormal tangent vectors.
  We can use these relationships to derive an expression for the jump in
  normal stress.
  \begin{align*}
    &({\bf T}_2\nnu)^+ - ({\bf T}_2\nnu)^-
    \\
    &= 2\rho^{-1} u_p^+v_p \nnu + 2\rho \nabla u_p^+ \cdot \nabla v_p
    \nnu
    - 2 \rho \nabla u_p^+  \nabla v_p \cdot \nnu
    - 2 \rho \nabla v_p  \nabla u_p^+ \cdot \nnu\\
    &-2\rho^{-1} u_p^-v_p \nnu - 2\rho \nabla u_p^- \cdot \nabla v_p \nnu
    + 2 \rho \nabla u_p^-  \nabla v_p \cdot \nnu
    + 2 \rho \nabla v_p  \nabla u_p^- \cdot \nnu\\
    &= 2\rho^{-1} \eta v_p \nnu + 2\rho \nabla \eta \cdot \tau_i \tau_i
    \cdot \nabla v_p \nnu
    - 2\rho \nabla \eta \cdot \tau_i \tau_i \nabla v_p \cdot \nnu + 0\\
    &= J_p.
  \end{align*}

  Applying the above relations to the integrand of \eqref{eq:prejump} yields
  \[
  ({\bf U}_2\nnu)^+ - ({\bf U}_2\nnu)^-
  =
  ({\bf I} + i {\bf X})(({\bf T}_2\nnu)^+ - ({\bf T}_2\nnu)^-)
  = ({\bf I} + i {\bf X})J_p
  \]
  This completes the proof of \eqref{eq:recipforcetorque}.
\end{proof}

\bibliographystyle{jfm}
\bibliography{reference}% Produces the bibliography via BibTeX.
